\documentclass[a4paper,11pt]{article}
\title{Shubham Rawat Resume}
\author{Shubham Rawat}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSummaryItem}{\item\small{\vspace{-3pt}}}

\newcommand{\resumeExperienceItem}{\item\small\vspace{-2pt}}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
  \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}





%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/rawat-shubham/}{\Large Shubham Rawat}} & Email : \href{mailto:shubham8456@outlook.com}{shubham8456@outlook.com} \\
  \href{https://www.linkedin.com/in/rawat-shubham/}{LinkedIn: Shubham Rawat} & Mobile : \href{tel:+919639304451}{+91-963-930-4451} \\
  \href{https://github.com/shubham8456/}{GitHub: github.com/shubham8456}
\end{tabular*}





%-----------SUMMARY-----------------
\section{Summary}
  \begin{itemize}
    \resumeSummaryItem Over 2.5+ years of experience developing applications using ruby, python, java, javascript.
    \resumeSummaryItem Extensive experience with different AWS services (Lambda, DynamoDB, Bedrock, S3, EC2, SQS) and Docker for containerization.
    \resumeSummaryItem Enhanced and maintained a RASA framework based chatbot, and worked on multiple generative AI projects using AWS Bedrock, OpenAI and LangChain.
    \resumeSummaryItem Strong understanding of Object-Oriented Programming and SOLID principles.
    \resumeSummaryItem Skilled in Test-Driven Development, ensuring comprehensive test coverage and defect-free code.
    \resumeSummaryItem Experienced in utilizing the Agile Scrum framework, adhering to its best practices for optimal project delivery.
  \end{itemize}





%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {PlanSource India Operations Pvt. Ltd.}{Bengaluru, India}
      {Associate Software Engineer (Full-time)}{August. 2023 - Present}
      \resumeItemListStart
        \resumeExperienceItem{Designed and implemented end-to-end architecture for various projects, collaborating with cross-functional teams to develop and deploy web applications. Handled both back-end and front-end tasks, developed new APIs, ensured 100\% test coverage, and managed front-end development using JavaScript and CSS.}
        \resumeExperienceItem{Enhanced a RASA-based chatbot with features for password resets, username retrieval, and user queries, allowing users to easily obtain information without navigating the UI.}
        \resumeExperienceItem{Integrated an LLM-based GenAI model into business dashboards, creating a chatbot that allows users to obtain insights by querying the dashboard data directly.}
        \resumeExperienceItem{Collaborated with the AWS team in a workshop to develop a smart agent designed to assist users in selecting their benefits. The agent utilized user demographics and survey responses to make informed decisions, enhancing the user experience by providing personalized and accurate benefit recommendations.}
        \resumeExperienceItem{Developed an admin chatbot capable of answering platform-specific questions and automating system tasks/jobs. My contribution was in creating the AI agent and supporting back-end APIs.}
        \resumeExperienceItem{Implemented and integrated Superset, an open-source BI and visualization tool, into the product, resulting in savings of over \$200k.}
        \resumeExperienceItem{Automated ETL pipelines and ecosystem integrations on the Tray.io platform, managing crucial data for high-revenue clients.}
        \resumeExperienceItem{Brainstormed and developed GenAI initiatives as part of a research team, including a summary generation tool and a data extraction system. These features were integrated into the product, making it a differentiator from our rivals and simplifying user tasks.}
      \resumeItemListEnd

    \resumeSubheading
      {MountBlue Technologies Pvt. Ltd.}{Bengaluru, India}
      {Software Development Engineer (Contract - PlanSource)}{August. 2022 - July. 2023}
      \resumeItemListStart
        \resumeExperienceItem{Established a comprehensive testing framework which ensured accurate data transfer via crucial APIs.}
        \resumeExperienceItem{Developed an event-driven system using AWS SQS and Lambdas for processing and transmitting bulk data to business partners.}
        \resumeExperienceItem{Implemented CI/CD pipelines to ensure only defect-free code is deployed to servers through automated testing and code deployment.}
        \resumeExperienceItem{Contributed to monolithic and microservices architecture in Ruby and JavaScript, while ensuring error-free code in tightly coupled systems.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------





%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {College of Engineering Roorkee}{Roorkee, India}
      {Bachelor of Technology in Computer Science and Engineering;  Percentage: 67.30}{July. 2014 -- June. 2018}
    \resumeSubheading
      {Doon International School}{Dehradun, India}
      {XII CBSE;  Percentage: 84.60}{April. 2012 -- May. 2013}
  \resumeSubHeadingListEnd





%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeItemListStart
    \resumeItem{Languages}
      {Javascript, Ruby, Python, Java, SQL}
    \resumeItem{Technologies}
      {AWS Cloud products (EC2, S3, SQS, OpenSearch, Lambda, API Gateway), Databases (mySQL, Postgres, Snowflake, Redis, AWS DynamoDB), Docker, RASA, LangChain, OpenAI API, Web frameworks (Rails, FastApi, ReactJS, Spring), tray.io, pendo.io}
  \resumeItemListEnd





%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Instagram Clone}
      {Instagram clone web app. having features to follow other users and see their posts; and like and comment on them. App was hosted on AWS EC2 machine and user uploads were stored on AWS S3. The users could sign up and use the social media app as per their authorization.}
    \resumeSubItem{Flight Booking web app}
      {Flight booking app where a admin can create flight schedules and users can book flights for themselves. Used postgres to store data.}
    \resumeSubItem{Fundraiser website frontend}
      {Fundraiser website where users can see the goals of the organization and can donate for the cause. Implemented just the frontend to learn UI for websites.}
  \resumeSubHeadingListEnd





%-------------------------------------------
\end{document}
